Synthesizing Symmetric Lenses

### 2019-02-28 papers/SymmetricLenses/main.tex
More comments

However, the set of real-world use cases for bijective lenses, where two
data formats contain different arrangements of precisely the same
information, is  
limited.  Oftentimes, two data
formats share just {\em some} of their information content.  For instance,
two related database tables might share four out of five columns, but each
might have a different fifth column.  Or one ad-hoc system-configuration
file might include some format-specific metadata, such as a date or a
reference number, while the same configuration file on another operating
system does not.  Indeed among the 48 benchmark problems described in
Section \ref{sec:evaluation} below, all of the benchmarks taken from Flash
Fill~\cite{flashfill} and many of the benchmarks that synchronize between
two ad hoc file formats have this characteristic, 13 benchmarks in
total.  \bcp{I don't understand this.  We say that the non-bijective
  situation is ``more common,'' but we support this by saying that 13 out of
48 benchmarks (that we chose!) are non-bijective.  Or am I misreading??} \afm{I
think this is due, in part, to where we got the benchmarks (Augeas typically removes
little information). I do think that
it is more common, but I suppose I have no real data on that. I've updated
the wording to be ``safer''.}

>>>>

However, the set of real-world use cases for bijective lenses, where two
data formats contain different arrangements of precisely the same
information, is  
limited.  Oftentimes, two data
formats share just {\em some} of their information content.  For instance,
two related database tables might share four out of five columns, but each
might have a different fifth column.  Or one ad-hoc system-configuration
file might include some format-specific metadata, such as a date or a
reference number, while the same configuration file on another operating
system does not.  Indeed among the 48 benchmark problems described in
Section \ref{sec:evaluation} below, all of the benchmarks taken from Flash
Fill~\cite{flashfill} and many of the benchmarks that synchronize between
two ad hoc file formats have this characteristic, 13 benchmarks in
total.
